More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-02-01 2016-Weak-FH-Bisim/WeakBisim.tex
correction Lemma 5

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$
s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
$\\
We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
				{{\Post^1_p}\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
\TODO{from here simplify the double indices in beta and gamma}
such that  $\Pred^1_p \iff {\Pred^1_p}\!'
		\land {\Pred^1_p}\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post^1_p}\!'\uplus 
		{\Post^1_p}\!''$ where ${{\Post^1_p}\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta^2)_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				{\Post^2}''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred}\,'
		\land {\Pred^2}''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post^2}'\uplus 
		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta^2)_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
\TODO{a reprendere avec la nouvelle decomp ; add the v of visible}

$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
({\Pred_i^1}'\bigotimes_{i=0}^{i-1}\subst{{\Post_i^1}'})
\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'}))\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
$

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				{\Post^2}''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0\ldots (n_1+n_2+2)]\,\, Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences, where sequence  $k$ has length $n_k$,  as follows:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
\TODO{ Attention peut dire que ${{\Pred^1_p}''}, {{\Pred^2}''}$ are diffrent from previous one}\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_k)_j^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in {j\in (J\cap\Holes(Q))},\quad
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'_1-1)}\!\!(\beta^1_{ij})\,\dotcup\,(\set{\beta^2})_j\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(len-1)}\!\!\!(\beta^3_{ij})
\\
\Pred_k=\!\!\bigwedge_{i=0}^{(n'_1-1)}\!\!
{\Pred_i^1}''\land{\Pred^2}''\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post_i^1}''}\land \big(\!\!\!\!\!\bigwedge_{i=(n'+1)}^{(len-1)}\!\!{\Pred^3_i}''\subst{{\Post^2}''}\big)\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}\\
\Post_k=\big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(len-1)}{\Post^3_i}''\big)\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}
$\\

@@

\TODO{link gamma j 0 with the alpha k ; this ises the visible abstraction and the ewautaions of 1,2,3 decomposition}
For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0\ldots n]$.
Therefore, we can conclude that we have for all $k\in [0\ldots n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$

>>>>

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big(\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}(\subst{\Post^2}  \bigotimes_{j=0}^{i-1}\subst{\Post^3_i})\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\big)
$\\

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{(\Pred^1_p)}',  
				{(\Post^1_p)}'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{(\Pred^1_p)}''},  
				{{(\Post^1_p)}''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred^1_p \iff {(\Pred^1_p)}'
		\land {(\Pred^1_p)}''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={(\Post^1_p)}'\uplus 
		{(\Post^1_p)}''$ where ${{(\Post^1_p)}''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
				{(\Pred^1_p)}',  
				{(\Post^1_p)}'}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				{\Post^2}''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred}\,'
		\land {\Pred^2}''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post^2}'\uplus 
		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
({\Pred_i^1}'\bigotimes_{i=0}^{i-1}\subst{{\Post_i^1}'})
\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'}))\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
$

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				{\Post^2}''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0\ldots (n_1+n_2+2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences, where sequence  $k$ has length $n_k$,  as follows:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in {j\in (J\cap\Holes(Q))},\,
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred_k=\big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
{\Pred_i^1}''\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^1}''}\big)
\land{\Pred^2}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^1}''}\land\\
\mbox{~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\subst{{\Post^2}''}\Big)\bigotimes_{j=0}^{(i-1)}\subst{{\Post^3_j}''}\\
\Post_k=\Big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(n_k-1)}{\Post^3_i}''\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)
$\\

@@

\TODO{link gamma j 0 with the alpha k ; this ises the visible abstraction and the ewautaions of 1,2,3 decomposition}

From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover, we have: $\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0\ldots n]$.
Therefore, we can conclude that we have for all $k\in [0\ldots n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$
